---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

The package `"binomial"` is an [R](http://www.r-project.org/) package that intends to simulate a binomial experiment and create a distribution of probabilities associated with a certain number of successes in the experiment.  

## Motivation 

This package has been developed to create a binomial library that easily allows users to calculate probabilities of binomial random variables depict binomial experiments using plots.

## Installation

Install the development version from GitHub via the package `"devtools"`:

``` r
# development version from GitHub:
#install.packages("devtools") 

# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-ishiras98/binomial")

# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-ishiras98/binomial", build_vignettes = TRUE)
```

## Usage

```{r}

library(binomial)

# binomial probability
# examples of how the package works 

# probability of 2 successes in 5 trials, probability of success = 0.5
bin_probability(success = 2, trials = 5, prob = 0.5)

# binomial distribution which shows binomial probabilities associated with each number of successes when there are 5 trials 

bin_distribution(trials = 5, prob = 0.5)

# binomial cumulative distribution  

bin_cumulative(trials = 5, prob = 0.5)


# summary of a binomial random variable, with number of trials and probability of success given 

bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1

# mean of a binomial experiment with 10 trials and prob of success equal to 0.3

bin_mean(10, 0.3)

# variance of a binomial experiment with 10 trials and prob of success equal to 0.3

# mode(s) of a binomial experiment with 10 trials and prob of success equal to 0.3

bin_mode(10, 0.3)

```
